### 2022-11-14 NSF2022/Description/summary.tex

\subsection*{Intellectual Merit}
\vspace{-0.1in}
The purpose of this research is to reach interesting physical phenomena
with less computational cost than molecular dynamics, and account for
more general features that continuum theory misses. The main ingredient
is defining a nonlocal interaction through the solution of an elliptic
boundary value problem that has the phenomenological characteristics of
long-range hydrophobic attraction. This minimal model, while intuitive,
is quite a general description of amphiphiles in solvent and gives rise
to rich phenomena from Janus particle aggregates to correctly predicting
elastic properties of bilayer. The technical research tasks include
quantifying collective properties of amphiphilic ensembles, improving on
mathematical models, efficient, high-order numerical algorithms for
large-scale simulations, and incorporating external fields through
electric charge.

>>>>

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of granules. The main
ingredient is a nonlocal interaction through the solution of an moving
domain elliptic PDE that encompasses long-range amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-known vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
amphiphilic ensembles, improving on mathematical models, efficient,
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory for the collective dynamics.

%The purpose of this research is to reach interesting physical phenomena
%with less computational cost than molecular dynamics, and account for
%more general features that continuum theory misses. The main ingredient
%is defining a nonlocal interaction through the solution of an elliptic
%boundary value problem that has the phenomenological characteristics of
%long-range hydrophobic attraction. This minimal model, while intuitive,
%is quite a general description of amphiphiles in solvent and gives rise
%to rich phenomena from Janus particle aggregates to correctly predicting
%elastic properties of bilayer. The technical research tasks include
%quantifying collective properties of amphiphilic ensembles, improving on
%mathematical models, efficient, high-order numerical algorithms for
%large-scale simulations, and incorporating external fields through
%electric charge.
